---
title: "Simple document"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
date: "2022-09-12"
---

```{r, message=FALSE}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from a _normal distribution_:

```{r chunk_name}
samp = rnorm(100)
length(samp)
```

I can take the mean of the sample, too!
The mean is `r mean(samp)`. 

```{r chunk_scatterplot, echo=FALSE}
plot_df = tibble(
  x = rnorm(n = 1000),
  y = 1 + 2 * x + rnorm(1000)
)

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```


# Customize Code Chunks: 

`eval = FALSE`: code will be displayed but not executed; results are not included.

echo = FALSE: code will be executed but not displayed; results are included.

include = FALSE: code won’t be executed or displayed.

message = FALSE and warning = FALSE: prevents messages and warnings from being displayed.

results = hide and fig.show = hide: prevents results and figures from being shown, respectively.

collapse = TRUE: output will be collapsed into a single block at shown at the end of the chunk.

error: errors in code will stop rendering when FALSE; errors in code will be printed in the doc when TRUE. The default is FALSE and you should almost never change it.

dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. 

```{r learning_assessment_1}

df <- tibble(
x = rnorm(500, mean = 1),
y = (x > 0),
z = abs(x)
)

ggplot(df, aes(x = z)) + geom_histogram()

med = median(df$z)
```
The median of the absolute values is `r round(med, digits = 2)`.

* The mean of the sample is `r mean(pull(df, x))`.
* The median of the sample is `r median(pull(df, x))`.
* The standard deviation of the sample is `r sd(pull(df, x))`.


# Formatting Text
Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

# YAML & Output Formats

author: "Jeff Goldsmith"
date: 2019-09-10

output:
  html_document:
    toc: true
    toc_float: true
    
output:
  pdf_document: default
  
output:
  word_document: default


